Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-22 paper/paper.tex
moved camera pictures figure. added pantilt figures
fixed merge with amanda's multicol commit

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\hyphenation{auto-nomous}

@@

The team is made of 12 Rutgers undergraduates
% List, can we do itemize for this? two columns? needs to be smaller
Anthony Garrison, President
Amanda Gaetano, Vice President
Pat Hickey, Treasurer and Electronics Team Leader
Greg Quinn, Mechanical Team Leader
Stephen Indyk, Cogan Noll, John Palmer, Adrien Perkins, Michael Varga, Bradley Lord, David Wescott, and Taras Wallace.

@@

\subsection{Camera}

MICHAEL : physical specification of camera (size, 5 megapixel stills). We selected it because...

@@

\subsection{Pan Tilt Unit}
\begin{figure}
	\centering
	\subfloat[Front View]{\label{fig:camera_frontview} 
			\includegraphics[width=0.3\textwidth]{../images/camera_frontview.jpg}}
	\subfloat[Isometric View]{\label{fig:camera_isometric} 
			\includegraphics[width=0.3\textwidth]{../images/camera_isometric.jpg}}
	\caption{Sony MHS-PM5. Image Credit: Sony}
	\label{fig:camera}
\end{figure}

\begin{figure}

\end{figure}

>>>>

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\usepackage{float}
\usepackage{textcomp}
\usepackage{multicol}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\hyphenation{auto-nomous}

@@

The team is made of 12 Rutgers undergraduates
% List, can we do itemize for this? two columns? needs to be smaller

\begin{multicols}{2}
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
%	\centering
	\item Anthony Garrison, President
	\item Amanda Gaetano, Vice President
	\item Pat Hickey, Treasurer and Electronics Team Leader
	\item Greg Quinn, Mechanical Team Leader
%\end{itemize}
%\begin{multicols}{2}
%\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
%	\centering
	\item Stephen Indyk 
	\item Cogan Noll
	\item John Palmer 
	\item Adrien Perkins
	\item Michael Varga 
	\item Bradley Lord
	\item David Wescott
	\item Taras Wallace
\end{itemize}
\end{multicols}

@@

\subsection{Camera}
\begin{figure}
	\centering
	\subfloat[Front View]{\label{fig:camera_frontview} 
			\includegraphics[width=0.3\textwidth]{../images/camera_frontview.jpg}}
	\subfloat[Isometric View]{\label{fig:camera_isometric} 
			\includegraphics[width=0.3\textwidth]{../images/camera_isometric.jpg}}
	\caption{Sony MHS-PM5. Image Credit: Sony}
	\label{fig:camera}
\end{figure}
MICHAEL : physical specification of camera (size, 5 megapixel stills). We selected it because...

@@

\subsection{Pan Tilt Unit}

\begin{figure}
	\centering
	\subfloat[Isometric View]{\label{fig:pantilt_isometric} 
			\includegraphics[width=0.9\textwidth]{../images/pantilt_isometric.png}}
\\
	\subfloat[Side View]{\label{fig:pantilt_side} 
			\includegraphics[width=0.9\textwidth]{../images/pantilt_side.png}}
	\caption{Pan Tilt Unit}
	\label{fig:pantilt}
\end{figure}
\begin{figure}
	\subfloat[Linkage Detail View]{\label{fig:pantilt_linkdetail} 
			\includegraphics[width=0.6\textwidth]{../images/pantilt_linkdetail.png}}
	\subfloat[Linkage Velocity Plots]{\label{fig:pantilt_linkdetail} 
			\includegraphics[width=0.4\textwidth]{../images/pantilt_linkplot.png}}
	\caption{Tilt Linkage Detail}
	\label{fig:pantilt_link}
\end{figure}
